Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-23 supplement.tex
Put all supmat pics in place

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/69}}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/example_18/314/errors.png}
  \caption{Equal mutation rate}
\end{figure}

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/70}}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/314/errors.png}
  \caption{Per-nucleotide mutation rate of 0.0125}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/315/errors.png}
  \caption{Per-nucleotide mutation rate of 0.025}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/316/errors.png}
  \caption{Per-nucleotide mutation rate of 0.05}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/317/errors.png}
  \caption{Per-nucleotide mutation rate of 0.1}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/318/errors.png}
  \caption{Per-nucleotide mutation rate of 0.2}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/319/errors.png}
  \caption{Per-nucleotide mutation rate of 0.4}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/example_24/320/errors.png}
  \caption{Per-nucleotide mutation rate of 0.8}
\end{figure}

>>>>

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/errors.png}
  \caption{Equal mutation rate}
\end{figure}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_1.png}
  \caption{Per-nucleotide mutation rate of 0.0125}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_2.png}
  \caption{Per-nucleotide mutation rate of 0.025}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_3.png}
  \caption{Per-nucleotide mutation rate of 0.05}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_4.png}
  \caption{Per-nucleotide mutation rate of 0.1}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_5.png}
  \caption{Per-nucleotide mutation rate of 0.2}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_6.png}
  \caption{Per-nucleotide mutation rate of 0.4}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_7.png}
  \caption{Per-nucleotide mutation rate of 0.8}
\end{figure}
